Probing internal structure of distant quasars using Microlensing

### 2014-03-20 paper1/theory.tex
whatever
Partially included the half-light radii equations
minor change
t

@@

@@

@@

\begin{figure}
\includegraphics[bb = 0 0 600 400]{lightcurve_crescent_1.pdf}
\caption{Lightcurve 1.}
\end{figure}

@@

\begin{figure}
\includegraphics[bb = 0 0 600 400]{lightcurve_gaussian_1.pdf}
\caption{Lightcurve 2.}
\end{figure}

@@

\begin{figure}
\includegraphics[bb = 0 0 600 400]{lightcurve_disc_1.pdf}
\caption{Lightcurve 3.}
\end{figure}

>>>>

For a gaussian distributed surface brightness source the half-light radius is directly proportional to the parameter $\sigma$ according to the equation:
\begin{equation}
r_{1/2} = \sqrt{ln(4)} \sigma.
\end{equation}

@@

The half-light radius of a uniform disk source is $R/\sqrt{2}$.

@@

The half-light radius of any source is invariant to any rotational transformation. In the present case of a crescent source the effective radius is dependent on the parameters $R_p$, $R_n$ and $\sqrt{a^2+b^2}$ exclusively. From symmetry considerations the centroid of the source is colinear with the centers of the two disks and it is situated at a distance $d_c$ from the center of the brigth disk. $d_c$ can be computed numerically by solving the equation:

\begin{equation}
\frac{S_0^C}{2} =  
\end{equation}

@@

\begin{figure}
\includegraphics[width = .8\textwidth]{lightcurve_gaussian_1.png}
\caption{Lightcurve 1.}
\end{figure}

@@

\begin{figure}
\includegraphics[width = .8\textwidth]{lightcurve_disc_1.png}
\caption{Lightcurve 2.}
\end{figure}

@@

\begin{figure}
\includegraphics[width = .8\textwidth]{lightcurve_crescent_1.png}
\caption{Lightcurve 3.}
\end{figure}
